---
title: "HTML Widgets Showcase"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    social: menu
    source: embed
    theme: yeti
---

```{r setup, include=FALSE}
library(flexdashboard)
```

### Leaflet is a JavaScript library for creating dynamic maps that support panning and zooming along with various annotations.

```{r message=FALSE, warning=FALSE}

library(pacman)
pacman::p_load (gsheet,ggthemes,ggplot2,dplyr,reshape2,grid,devtools,gridExtra,extrafont,lattice,png,curl,TeachingDemos,pastecs,scales)

ii <- data.frame(gsheet2tbl("https://docs.google.com/spreadsheets/d/1LtNkmJpLy4nua9raN0vmytced9rhnP-buKgT_PTJ3iE/edit?usp=sharing"))
fourteen<- ii %>% group_by(ageID) %>% summarise(total=sum(count))
colnames(fourteen)<-c("age","total") 
fourteen<-fourteen[1:30,]

mpg <- data.frame(gsheet2tbl("https://docs.google.com/spreadsheets/d/1pS_jCOMXdeHPztkEyyhWzaQL4OV1x8520_ILFv66XCk/edit?usp=sharing"))
mpg<-mpg[2:31,]
data<-merge(mpg,fourteen, by="age")
data$Perc <- data$total / sum(data$total) * 100

g.bottom <- ggplot(data, aes(x = age, y = Perc)) +
  geom_bar(stat="identity", fill="black") +
  theme_economist() + 
  theme(plot.margin = unit(c(0,5,30,30),units="points"),axis.title.y = element_text(vjust =3,size=9,face="bold"), axis.title.x = element_text(vjust=-1,size=10,face="bold"),axis.text.x=element_text(size=8,face="bold"), axis.text.y = element_text(size=8,face="bold"),
        panel.background=element_rect(fill="#a7c1a6"), plot.background=element_rect(fill="#a7c1a6"))+
  scale_x_continuous(breaks=0:29)+
  scale_y_continuous(limits=c(0,7),breaks=1:7,labels=c("1 %","2 %","3 %","4 %","5 %","6 %","7 %"))+
  labs(y = "Percentage of All Vehicles in Fleet",x = "Average Vehicle Age (Years)")

g.top <- ggplot(data, aes(x = age, y = miles.per.gallon)) +
  geom_line(size=1) +
  geom_point(size=3)+
  geom_point(size=1,color="white")+
  theme_economist() +
  scale_x_continuous(breaks=0:29)+
  scale_y_continuous(limits=c(27,37),breaks=c(27,29,31,33,35,37),labels=c("27 mpg","29 mpg","31 mpg","33 mpg","35 mpg","37 mpg"))+ggtitle("Fuel Economy and Age Distribution of Vehicle Fleet (2014)")+
  theme(plot.margin = unit(c(1,5,-10,30),units="points"), axis.title.y = element_text(vjust =3,size=9,face="bold"),plot.title = element_text(vjust=-.5,hjust=.8,size=12, face="bold"),axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.line.x=element_line(size=1),panel.background=element_rect(fill="#a7c1a6"), plot.background=element_rect(fill="#a7c1a6"),
         axis.text.y = element_text(size=8,face="bold"))+
  labs( y = "Fuel Economy (MPG)")

grid.arrange(g.top,g.bottom, heights = c(1/2, 4/5))

```

***

https://rstudio.github.io/leaflet/

- Interactive panning/zooming

- Compose maps using arbitrary combinations of map tiles, markers, polygons, lines, popups, and GeoJSON.

- Create maps right from the R console or RStudio

- Embed maps in knitr/R Markdown documents and Shiny apps

- Easily render Spatial objects from the sp package, or data frames with latitude/longitude columns

- Use map bounds and mouse events to drive Shiny logic


### d3heatmap creates interactive D3 heatmaps including support for row/column highlighting and zooming.

```{r message=FALSE, warning=FALSE}

library(pacman)
pacman::p_load(ggplot2, grid, gridExtra,cowplot, ggthemes,scales,dplyr,devtools, plotly, RColorBrewer) 

setwd("X:/Trans/STAFF/Reid/Project Selection/countywide data viz")
forms<- read.csv("screening forms all.csv")
forms$total_requested <- rowSums(forms[,c("Funding.request.one.amount", "Funding.request.two.amount")], na.rm=T)
forms$sc_app<-"screening form"
apps<-read.csv("funding applications no king.csv")
apps$total_requested <- rowSums(apps[,c("Funding.request.one.amount", "Funding.request.two.amount")], na.rm=T)
apps$sc_app<-"application"
apps$count<-1
forms <- select(forms, Competition, Psrc.funding.source,Project.title,total_requested, sc_app)
apps1 <- select(apps, Competition, Psrc.funding.source,Project.title,total_requested, sc_app)
data<-rbind(forms,apps1)

data2<-data %>% 
  group_by(Competition, sc_app) %>%
  summarise(submissions=n(), total_requested=sum(total_requested))

data2$sc_app <- factor(data2$sc_app, levels=c("screening form", "application"))


ggplot(data2, aes(x=Competition, y=total_requested, fill=factor(sc_app))) +
  geom_bar(stat="identity", position="dodge", alpha=.75) +
  scale_fill_manual(values=c("#2E9AFE", "#0B3861")) +
  theme_economist_white(gray_bg=FALSE) +
  theme(legend.position = "none",axis.title.y=element_text(size=18,face="bold", margin=margin(0,20,0,0)),axis.title.x=element_blank(),axis.ticks.x=element_blank(), 
        axis.text.y=element_text(face='bold'),axis.text.x=element_text(face='bold', size=12)  ) +
  scale_y_continuous(limits=c(0,200900000), breaks=seq(0, 200900000, by=40000000), labels=c("$ 0", "$ 40M", "$ 80M", "$ 120M", "$ 160M", "$ 200M"))+
  annotate("rect", xmin=3.45, xmax=4.35, ymin=190000000, ymax=200000000,  color="black", fill=NA,linetype=5, size=.5) +
  annotate("rect", xmin=3.45, xmax=4.35, ymin=170000000, ymax=180000000,  fill="#2E9AFE", alpha=.75) +
  annotate("text", x = 3.9, y=175000000, label = "SCREENING FORMS", color="white", size=4, fontface="bold")+
  annotate("text", x = 3.9, y=195000000, label = "AMOUNT AVAILABLE", color="black", size=3.5, fontface="bold")+
  annotate("rect", xmin=3.45, xmax=4.35, ymin=190000000, ymax=180000000,  fill="#0B3861", alpha=.75) +
  annotate("text", x = 3.9, y=185000000, label = "APPLICATIONS", color="white", size=4, fontface="bold") +
  annotate("text", x = 3.38, y=165000000, label = "* Number of Applications/Forms Submitted", color="black", size=4.5, fontface="bold") +
  geom_text(aes(x=Competition,y=4000000,label=paste(submissions, "*")),size=4.5,fontface='bold',color="black", position = position_dodge(width = 1)) +
  geom_text(aes(x=Competition,y=total_requested,label=paste("$",substr(total_requested, 1, nchar(total_requested)-6), "M" )), 
            size=4.5,fontface='bold', color="white", position = position_dodge(width = 1), vjust=1.7) +
  labs(y="Amount Requested")+
  annotate("text", x = 3.9, y=-10, label = "Screening Forms", color="black", size=4, fontface="bold") +
  scale_x_discrete(labels=c("King Countywide" = "King County \r\n $67.96M available", "Kitsap Countywide" = "Kitsap County \r\n $12.34M available "
                            ,"Pierce Countywide" = "Pierce County \r\n $25.48M available","Snohomish Countywide" = "Snohomish County \r\n $25.08M available")) +
  annotate("rect", xmin=.55, xmax=1.45, ymin=0, ymax=68000000,  color="black", fill=NA,linetype=5, size=.5,alpha=.5) +
  annotate("rect", xmin=1.55, xmax=2.45, ymin=0, ymax=13000000,  color="black", fill=NA,linetype=5, size=.5,alpha=.5) +
  annotate("rect", xmin=2.55, xmax=3.45, ymin=0, ymax=26000000,  color="black", fill=NA,linetype=5, size=.5,alpha=.5) +
  annotate("rect", xmin=3.55, xmax=4.45, ymin=0, ymax=26000000,  color="black", fill=NA,linetype=5, size=.5,alpha=.5) 
  

```


***

https://github.com/rstudio/d3heatmap/

- Highlight rows/columns by clicking axis labels

- Click and drag over colormap to zoom in (click on colormap to zoom out)

- Optional clustering and dendrograms, courtesy of base::heatmap


### Dygraphs provides rich facilities for charting time-series data in R and includes support for many interactive features.

```{r}
library(pacman)
pacman::p_load(xlsx,ggplot2, ggthemes,scales,grid,gridExtra,dplyr,tidyr,plotly,extrafont)

setwd("X:/Trans/STAFF/Reid/Project Selection/EJ Analysis")

data<-read.xlsx("DemogDataEJ.xlsx", sheetName="DemogDataEJ")

data$pct_eld_whole<-data$pct_eld * 100
data$pct_dis_whole<-data$pct_dis * 100
data$pct_pov_whole<-data$pct_pov * 100
data$pct_min_whole<-data$pct_min * 100

ggplot(data, aes(pct_min_whole)) + geom_histogram(binwidth=1, colour="white", fill="#F05A28", alpha=0.7) + theme_economist() + 
    theme(plot.background=element_rect(fill = alpha("#00A7A0", 0.25), colour="white"), panel.background=element_blank(),axis.text.y=element_text(color="black", face="bold",size=16),
          axis.text.x=element_text(color="black", face="bold",size=16),axis.title.x=element_text(color="black", face="bold",margin=margin(20,0,0,0),size=16) ,
          axis.title.y=element_text(color="black", face="bold",margin=margin(0,20,0,0),size=16) ) + 
    annotate("segment", x=33.1, xend = 33.1, y=0, yend=33,colour= "#91268F", linetype="longdash", size=1)+
    annotate("segment", x=47, xend = 62.5, y=26, yend=26,colour= "#91268F", linetype="longdash", size=1)+
    annotate("text", x=55, xend = 55, y=25, yend=25,label="REGIONAL THESHOLD",colour= "#91268F", fontface="bold",size=6)+
   ylab("NUMBER OF CENSUS TRACTS") +xlab("PERCENT MINORITY PER CENSUS TRACT") +
    scale_x_continuous(breaks=c(0,10,20,30,40,50,60,70,80,90,100),labels=c("0","10%","20%","30%","40%","50%","60%","70%","80%","90%","100%"))
```

***

https://rstudio.github.io/dygraphs/

- Automatically plots xts time series objects (or any object convertible to xts).

- Highly configurable axis and series display (including optional second Y-axis).

- Rich interactive features including zoom/pan and series/point highlighting.

- Display upper/lower bars (e.g. prediction intervals) around series.
- Various graph overlays including shaded regions, event lines, and point annotations.


### Plotly provides bindings to the plotly.js library and allows you to easily translate your ggplot2 graphics into an interactive web-based version.

```{r}
#load required packages
library(pacman)
pacman::p_load(scales,knitr,grid, gridExtra,ggthemes,gsheet,RCurl,dplyr, xlsx, RODBC, ggmap, foreign, maptools, rgdal, ggplot2, devtools, broom, sp, maps, mapdata, googlesheets)

#load data from google sheets
data <- data.frame(gsheet2tbl("https://docs.google.com/spreadsheets/d/1tVtrA8s1iv19OKXAmShSqQcT71zT7_DOk0ICsm8brrE/edit?usp=sharing"))
pop <- data.frame(gsheet2tbl("https://docs.google.com/spreadsheets/d/1xLc8rCkzZp5pqVh8LKzB9bsyeDNmnUXiZciAgvqOE88/edit?usp=sharing"))

#summarise data
data_sum<-data %>% 
  group_by(Sponsor, ID, Title, Total.Project.Cost) %>%
  summarise(psrc_funds = sum(PSRC.Funds), phases=paste(Phase.s., collapse=" & "))

#join datasets
data_final<-left_join(pop, data_sum, by="ID") %>% select (X2010.Population, ID, phases.y, psrc_funds, Sponsor.y, Title.y)

#clean data
data_final<-data_final[complete.cases(data_final),]
data_final$X2010.Population<-gsub(",","",data_final$X2010.Population)
data_final$X2010.Population<-as.numeric(data_final$X2010.Population)

#manipulate data
data_final <- data_final %>% mutate (jurisdiction_size= ifelse(X2010.Population <50000, "Small Size Jurisdiction", ifelse(X2010.Population >= 50000 & X2010.Population < 100000, "Medium Size Jurisdictions",ifelse(X2010.Population >= 100000 & X2010.Population < 300000, "Large Size Jurisdiction", ifelse(X2010.Population >= 300000 , "Largest Size Jurisdiction", "Not Applicable")))))

#prepare data for display in table
data_final<-data_final[order(data_final$psrc_funds),]
data_final$jurisdiction_size[is.na(data_final$jurisdiction_size)] <- "Transit Agency"
data_graph<-data_final
data_graph<-data_graph %>% filter(phases.y %in% c("CN","CN & BUSR & OTH","OTH", "PE", "PE & CN", "PE & ROW", "PE & ROW & CN"))
data_final$psrc_funds<-dollar(data_final$psrc_funds)
colnames(data_final)<- c("Population", "ID","Phases", "Funding Award", "Jurisdiction", "Project Title", "Size")
data_final<-data_final %>% select(Population, `Funding Award`, Jurisdiction, `Project Title`, Size)
data_final$Population<-prettyNum(data_final$Population,big.mark=",",scientific=FALSE)
data_final$Population<- gsub("NA","Transit Agency", data_final$Population)
data_final<-data_final[c("Jurisdiction", "Project Title", "Funding Award", "Population", "Size")]

#show summary table
kable(data_final[1:10, ], caption = "Smallest Funding Amounts Per Project", row.names=FALSE, align='l')

ggplot(data_graph, aes(jurisdiction_size, psrc_funds, fill=phases.y)) +geom_bar(stat="identity") +theme_economist() +coord_flip() + theme( axis.title.y = element_blank(), legend.title = element_blank(), plot.background = element_rect(fill="#afccb7"),panel.background = element_rect(fill="#afccb7"), legend.background =element_rect(fill="#afccb7")) +ylab("Federal Funds Awarded") + scale_fill_manual(values=c("#067ca0", "#9e3838","#c17913","#258227","#653e7c","black","#8c8b7f")) +scale_y_continuous(labels=scales::dollar)

```

***

https://plot.ly/ggplot2/

If you use ggplot2, `ggplotly()` converts your plots to an interactive, web-based version! It also provides sensible tooltips, which assists decoding of values encoded as visual properties in the plot.

plotly supports some chart types that ggplot2 doesn't (such as 3D surface, point, and line plots). You can create these (or any other plotly) charts using `plot_ly()`.


### MetricsGraphics enables easy creation of D3 scatterplots, line charts, and histograms.

```{r}
library(metricsgraphics)
mjs_plot(mtcars, x=wt, y=mpg) %>%
  mjs_point(color_accessor=carb, size_accessor=carb) %>%
  mjs_labs(x="Weight of Car", y="Miles per Gallon")
```

***

https://hrbrmstr.github.io/metricsgraphics/

Building metricsgraphics charts follows the “piping” idiom made popular through the magrittr, ggvis and dplyr packages. This makes it possible to avoid one giant function with a ton of parameters and facilitates breaking out the chart building into logical steps. 

While MetricsGraphics.js charts may not have the flexibility of ggplot2, you can build functional, interactive [multi-]line, scatterplot, bar charts & histograms and + even link charts together.